Tree-based

### 2023-12-13 Tree.Rmd
Removed N_days from tree formula

```{r}
# Grow Graduate tree via rpart package
library(rpart)
rPartStatus <- rpart(
  formula = Status ~ N_Days + Drug + Age + Sex + Ascites + Hepatomegaly + Spiders + Edema + Bilirubin + Cholesterol + Albumin + Copper + Alk_Phos + SGOT + Platelets + Prothrombin + Stage + Tryglicerides, 
  data = trainingData,
  method = "class",
  parms = list(split = "information")
  # We did not need to use the control parameters
)

>>>>

```{r}
# Grow Graduate tree via rpart package
library(rpart)
rPartStatus <- rpart(
  formula = Status ~ Drug + Age + Sex + Ascites + Hepatomegaly + Spiders + Edema + Bilirubin + Cholesterol + Albumin + Copper + Alk_Phos + SGOT + Platelets + Prothrombin + Stage + Tryglicerides, 
  data = trainingData,
  method = "class",
  parms = list(split = "information")
  # We did not need to use the control parameters
)
